Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/type-theory.tex
Numbered all the examples.
[ paper ]  type-theory introduction.

% Type theory is a formalism [TODO]

% Even though we choose a proof-assistant for type theory
% where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.

@@

\begin{notation}
Types are written using small caps.
We write the type judgments as $m : \abbre{M}$ to denote
that $m$ has $\abbre{M}$ type.
We use \Prop for the type of propositions and the dependent type, $Γ ⊢ φ$ for
theorems where $Γ : \List~\Prop$ and $φ : \Prop$.
$\abbre{List}$ type is the usual inductive type for lists.
For syntactical equivalence, we write the equality as $φ ≡ ψ$
for $φ,~ψ : \Prop$. For this equality, we assume the
reflexivity, symmetry and transitivity properties.
\end{notation}

@@

\begin{myexample}
\label{ex:structural-recursion}

>>>>

Type theory is another formalism for the foundation of mathematics, and it has become in a key instrument to study logic and proof theory.
It was proposed in 1902 to avoid the Russell's paradox and it follows
the same philosophy of constructive mathematics where the witness of
a statement is \emph{everything}. In that direction, we could say
the main actors in type theory are the statements and their proofs.
The \emph{types} are theorems and their \emph{terms} are the proofs.

Since it is a formal system, in type theory, we have a syntax and a set of derivation rules. These rules enables us to get certain kind of conclusions that we call \emph{judgments}. A judgment is a statement that says a
term has certain type.

\begin{notation}
Types are written using small caps.
We write the type judgments as $m : \abbre{M}$ to denote
that $m$ has $\abbre{M}$ type.
\end{notation}

With the derivation rules we produce derivation trees inside
the judgments. These trees represent proofs of theorems.
We use such level of expressiveness for the reconstructed proofs
from the \ATPs.

% Since type theory can be seen as typed lambda calculus with dependent products,
% compute terms is basically $\beta$-reductions.
% And we

We choose a proof-assistant for type theory
because of the verification of proofs is type-checking, that is,
given a type of the theorem and the proof-term, verify that term
effectively has the type of the theorem.
Therefore, by following the Curry-Howard correspondence,

@@

\begin{notation}
We use \Prop for the type of propositions and the dependent type, $Γ ⊢ φ$ for
theorems where $Γ : \List~\Prop$ and $φ : \Prop$.
$\abbre{List}$ type is the usual inductive type for lists.
For syntactical equivalence, we write the equality as $φ ≡ ψ$
for $φ,~ψ : \Prop$. For this equality, we assume the
reflexivity, symmetry and transitivity properties.
\end{notation}

@@

\begin{myexamplenum}
\label{ex:structural-recursion}
